Numerical investigation of low-load operation of a subcritical power boiler using CFD and process modelling

### 2021-10-20 PAPER_2/PAPER_2_REV1.tex
Update2 - 20/10/2021

%% Group authors per affiliation:
\author{B.T. Rawlins}
\author{R. Laubscher\corref{mycorrespondingauthor}}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{ryno.laubscher@uct.ac.za}
\author{P. Rousseau}
\address{Department of Mechanical Engineering, Applied Thermal-Fluid Process Modeling Research Unit, University of Cape Town, Library Rd, Rondebosch, Cape Town, 7701, South Africa}
\address{$^*$ Department of Mechanical Engineering, Stellenbosch University, Stellenbosch Central, Stellenbosch, 7599, South-Africa}

\begin{abstract}
This paper uses co-simulation techniques which incorporate a computational fluid dynamic (CFD) model together with a process level model to investigate the low-load operation of a 620 $MWe$ sub-critical boiler. A 1D discretized two-phase model of the water/steam circuit of the furnace, the radiant superheaters (SH) and the convective/back pass heat exchangers was developed. This was coupled with a detailed CFD model incorporating the furnace and radiant superheaters using an Eulerian-Eulerian reference frame. The coupled model is used to investigate the combustion stability, the water/steam side effects and the radiant heat exchanger operational limits for six burner firing arrangements for a minimal boiler load of 32 \%. The results show that certain firing arrangements can lead to a high possibility of fire-side corrosion and the over-heating of heat exchanging components. Based on the numerical simulations carried out in terms of obtaining combustion stability, a favourable boiler utilization efficiency and the safe operation of heat exchanging components, a mixed firing arrangement accompanied with a higher secondary air (SA) mass flow-rate for non-firing burners was selected as the best case for the boiler under investigation.
\end{abstract}

@@

\linenumbers

@@

The use of coal-fired power plants (CFPP) to provide electricity generation is intended to be phased out in order to mitigate the ingress of climate change. However, the switch to sustainable generation sources poses great challenges for developing countries due to the long transition times and costs involved \cite{ugum2019}. Due to the abundance of coal resource present in Southern Africa, CFPPs are the dominant power generation source, with approximately 80 \% of the energy needs being met using CFPPs \cite{eskom}. The promising integration of renewable energy and the decommissioning of old CFPPs in Southern Africa, will push these plants from a primarily base load operation to a mid-merit/flexible operating protocol. The switch to flexible operation will inherently mean CFPPs will need to operate at low-loads for continuous time periods.

Mathematical models that can accurately capture the thermal response of boilers at varying loads can be used to determine the safe and efficient operating limits \cite{Laubscher2019b}. Since, the long term deviation from design conditions can lead to operational inefficiencies affecting combustion stability \cite{Hernik2020}, an increase in harmful emissions \cite{Chang2021} and the localised overheating of heat exchangers due to insufficient cooling being provided by the internal working fluid \cite{Modlinski2019}.

The full scale testing or experimentation of CFPPs is deemed to expensive to pursue, thus the use of computational fluid dynamics (CFD) allows for the modelling of a full-scale CFPPs, at steady-state, to be investigated at various loads circumventing the use of time-consuming and costly field tests. CFD simulations have been successfully used to model a variety of CFPP boiler types (\cite{Laubscher2019a}, \cite{Gu2020}) and cover various aspects such as pollution control (\cite{Du2017},\cite{Fan2001}), gas-solid flow effects (\cite{Chen2017}) and boiler retrofitting (\citep{Gu2020}, \cite{He2007}).

Recent CFD studies investigating low-load operation of CFPP boilers have focused on the combustion stability, harmful emissions and the gas flow-solid flow interactions \cite{Jiang2021}. The works of Belosevic et al \citep{Belosevic2019a} found that the low-load operation of boiler considerably affect the flow and temperature fields, the flame geometry, chemical reactions and concentrations of combustion products.

Hernik et al \cite{Hernik2020} investigated the effects of using different mill system configurations at a minimum boiler load of 40 \%. The most favourable mill system configuration was selected based on the case that exhibited suitable combustion stability and emission of harmful substances. Similarly, Chang et al \citep{Chang2021} investigated the various firing arrangements of a 630 $MWe$ tangentially fired boiler. A burner angle of -15 $^\circ$ was found to be the optimal arrangement resulting in the best compromise in combustion stability and lower emissions. The aforementioned reseacrh specifically investigated combustion and gas-side effects. However, to the best the authors' knowledge, no integration of 1-D process model has been used to investigate the steam side operational performance of a CFPP boiler at low-load.

The use of a 1-D process modelling approach have been used by researchers to investigate the water and gas side heat transfer interactions. These studies are usually used to investigate a transient event, such as a sudden disturbance, start-up or boiler load ramping \cite{Alobaid2017}. Due to the non-uniformities found in CFPP furnaces which are composed of complex combustion dynamics, gas-solid interactions and  radiation heat transfer phenomena, 1-D process models can not resolve the fireside with sufficient accuracy, but can adequately resolve the waterside energy and momentum transport in a computationally inexpensive manner.

The use of coupled simulations has proven to solve the deficiencies of a full 1-D process model by coupling the fireside CFD results to a 1-D water side model. Some recent papers that investigated boiler operations using a co-simulation approach are: Laubscher and Rousseau \cite{Laubscher2020} conducted a comprehensive numerical study on the impact of particle radiation properties for high ash coals using ANSYS Fluent v19.2\textsuperscript{\textregistered} and Flownex SE\textsuperscript{\textregistered}. Yu et al \cite{Yu2019} used a coupled simulation methodology to estimate the superheater (SH) metal temperatures of a 660 $MWe$ tangentially-fired coal boiler.

The goal of the current work is to investigate the effect of burner firing configuration on various process parameters such as steam temperatures, spray water flow-rates and metal temperatures. The current work proposes the use of CFD modelling  to investigate the low-load gas-side effects at various firing conditions for a 620 $MWe$ two-pass sub-critical boiler. For the current work CFD gas-side results are coupled to a comprehensive process model of the case study boilers water side.

The model was simulated for a boiler load of 32 $\%$  with 6 various firing combinations. To establish the accuracy of the CFD modelling approach a validation study was conducted for 100 $\%$, 80 $\%$ and 60 $\%$ maximum continuous rating (MCR) loads and compared to actual plant measurements to quantify the model accuracy, this is highlighted in section \ref{sec_model_valid} prior to the results of the low-load study.

\section{Mathematical model}
In this section the modelling techniques used by the study are briefly discussed.
\subsection{Computational fluid dynamics modelling}
\subsubsection{Fluid flow, turbulence and combustion modelling}
The flue gas was modelled using a Eulerian framework. The species transport modelling approach was used to approximate the mixture of chemical species in the gas phase. This approach solves a species continuity equation for each constituent present in the mixture. To reduce the computational burden it was assumed that the various processes were in steady-state. The governing equations for the gas phase are written in their respective Reynolds averaged forms as follows;\\
Mass conservation:
\begin{equation}\label{eqn_RANS_mass}
\frac{\partial}{\partial x_{i}}(\rho \bar{u}_{i})=S_{m}.
\end{equation}
Momentum conservation:
\begin{equation}\label{eqn_momentum}
\frac{\partial}{\partial x_{i}}(\rho_{eff} u_{i}u_{j})+\frac{\partial \overline{p}}{\partial x_{j}}=\frac{\partial}{\partial x_{i}}\left[\mu\left\{\frac{\partial u_{j}}{\partial x_{i}}+\frac{\partial u_{i}}{\partial x_{j}}-\frac{2}{3}\delta_{ij}\frac{\partial u_{i}}{\partial x_{i}}\right\}\right]+\frac{\partial}{\partial x_{i}}(-\rho\overline{u_{i}^{'}u_{j}^{'}})+S_m
\end{equation}
Energy conservation:
\begin{equation}\label{eqn_energy}
\frac{\partial }{\partial x_{i}} (u_{i}[\rho E+p])=\frac{\partial }{\partial x_{j}}\left[\lambda\frac{\partial T_{g}}{\partial x_{j}}\right] +S_{h}
\end{equation}
Species transport:
\begin{equation}\label{eqn_species}
\begin{split}
&\frac{\partial}{\partial x_{i}}(\rho u_{j}Y_{k})=-\frac{\partial}{\partial x_{j}}(\vec{J_{k}})+ \sum_r R_{j,r} + S_{k}\\
&k = 1,2,3...N
\end{split}
\end{equation}
To correctly account for the particle inertial effects on the gas phase convection, the model makes use of an effective density which is defined as follows;
\begin{equation} \label{eqn_eff_rho}
	\rho_{eff} = \frac{\rho \rho_p \left( \phi_{mp} + 1 \right)}{\rho \phi_{mp} + \rho_p}
\end{equation}

In the present study the realizable k-$\epsilon$ turbulence model was utilized to address the turbulence closure problem. This model has been successfully used by researchers (\cite{Belosevic2019a},\cite{Laubscher2019a} and \cite{Modlinski2019}), in modelling the effects of coal-fired swirl burners. The model generally produces higher accuracy results, when compared to the standard k-$\epsilon$ model, for problems incorporating swirling and separating flows.

The process of coal combustion comprises of four sequential steps. Namely, inert heating and evaporation of moisture, devolatilization, char oxidation and gas phase reactions. Equations (\ref{eqn_vol_rate}) and (\ref{eqn_vol_arrhenuis}) show the single rate kinetic model utilized in this study, to model the devolatilization process.
\begin{gather}
\frac{dm_{vol}}{dt} = R_{vol}(m_{0,vol}-m_{vol}) \label{eqn_vol_rate} \\
\begin{split}
&R_{vol} = A_{vol}exp\left(\frac{E_{a,vol}}{RT_p}\right)\\
&A_{vol} = 2\times10^5 [s^{-1}]\,\,\,\,\,\,\,\,\,\,E_{a,vol} = 6.7\times10^7 [J/kmol] \label{eqn_vol_arrhenuis}
\end{split}
\end{gather}

A devolatilization temperature of 553 [$K$] \citep{Ranade2015} along with the kinetic parameters (equation \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized in the present study. The char oxidation process is modelled using the diffusion-kinetics limited model developed by Baum and Street \cite{Baum1971}, which is given in equation (\ref{eqn_char_rate}). The product species of the char oxidation reaction was set to $CO$ as shown in equation (\ref{eqn_CO_reaction}). 
\begin{gather}
\frac{dm_{char}}{dt} = -A_p p_{O_{2}} \frac{R_{diff}R_c}{R_{diff} + R_c}  \label{eqn_char_rate}\\
C_{(s)}+0.5O_{2(g)}\to CO_{(g)} \label{eqn_CO_reaction}
\end{gather}
The diffusion and kinetic rates of equation (\ref{eqn_char_rate}) are defined in equations (\ref{eqn_char_diff_rate})  and (\ref{eqn_char_kin_rate}) with the kinetic parameters again taken from the works of Sheng et al \citep{Sheng2004}.
\begin{gather}
R_{diff} = \frac{5\times10^{-12}}{d_p} \left(\frac{T_g+T_p}{2}\right)^{0.75} \label{eqn_char_diff_rate}\\
\begin{split}
&R_{c} = A_{c}exp\left(\frac{E_{a,c}}{RT_p}\right)\\
&A_{c} = 0.0053 [kg/m^2sPa]\,\,\,\,\,\,\,\,\,\,E_{a,c} = 8.37\times10^7 [J/kmol]
\end{split}
 \label{eqn_char_kin_rate}
\end{gather}

The turbulence-chemistry interactions of the gas phase reactions were approximated using the eddy-dissipation-finite rate model used in ANSYS Fluent v19.5\textsuperscript{\textregistered} which calculates three rates, namely chemical reaction rate, turbulent production eddies dissipation rate and reaction eddies dissipation rate, and uses the minimum of the three for the source terms calculations. A description of the CFD gas phase reactions of the boiler under consideration, using the same coal, was previously published in the works of Laubscher and Rousseau \cite{Laubscher2019b}.

\subsubsection{Particle modelling}
The particles are modelled using a Eulerian reference frame, similar to the studies of Knaus et al \cite{Knaus2001a} and Benim et al \cite{Benim2005}, who both successfully used a Eulerian-Eulerain (EE) model to capture the characteristics of coal combustion and furnace heat transfer with adequate accuracy. The pseudo particle mass concentrations transported into the domain are modelled using the general scalar field transport equation with the necessary modifications to account for heat and mass transport \cite{Versteeg2007}. The pseudo-particles scalar fields are used to define the fuel characteristics based on the proximate analysis composition, namely consisting of moisture, volatile matter, fixed  carbon and ash. Each of the scalar field equations are given in Table \ref{tab_scalars}.

@@

The energy transport of the pseudo particle phase, is transported by defining a particle phase energy equation, which in turn uses the particle enthalpy.
\begin{equation}\label{eqn_phi_hp}
\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{hp})=\left(f_{heat}\frac{dm_{c}}{dt}h_{rxn} + \dot{Q}_{rad} + \dot{Q}_{conv} - \frac{dm_{evap}}{dt}h_{fg}\right)\frac{1}{V}
\end{equation}

The equation accounts for all the processes associated with energy transport to the particle, namely convection $\left(\dot{Q}_{conv}\right)$, radiation $\left(\dot{Q}_{rad}\right)$, latent heat transport $\left(\frac{dm_{evap}}{dt}h_{fg}\right)$ and near surface char oxidation $\left(f_{heat}\frac{dm_{c}}{dt}h_{rxn}\right)$. This gives the model the ability to track the particle temperature in the domain, moving the model away from the thermal equilibrium approach incorporated by previous studies using an EE approach (\cite{Benim2005}, \cite{Vicente2003} and \cite{Cai2015}). The particle temperature is important in describing the sequential steps found in modelling combustion processes, especially at low boiler loads where mixing and ignition become problematic. To solve the additional transport equations and their source terms, C programs were developed.

\subsection{Heat transfer modelling modelling}
Radiation heat transfer is the dominant form of heat transfer found in industrial furnaces \citep{Basu2000} and is solved by applying the gray-participating-gas and particle medium configuration of the radiation transport equation (RTE) \cite{Modest2013} shown in equation (\ref{eqn_RTE}).
\begin{equation}\label{eqn_RTE}
\frac{d I(\vec{r},\hat{s})}{ds} = \alpha_g \frac{\sigma_{SB} T_{g}^4}{\pi}-(\alpha_g+\alpha_p+\sigma_p)I(\vec{r},\hat{s}) + \frac{\sigma_p}{4\pi}\int_{4\pi}I(\vec{r},\hat{s})\Phi d \Omega
\end{equation}
In the present work the RTE is solved using the P1 model. Ranade and Gupta \cite{Ranade2015} illustrated minimal differences between the two common radiation models (namely the P1 and discrete ordinates (DO)) for the resultant wall heat transfer rate values when modelling a 210 $MWe$ CFPP boiler. The P1 radiation model can include the effects of particle absorption ($\alpha_p$) and scattering ($\sigma_p$) as well as gas mixture absorption ($\alpha_g$). The P1 model transport variable is the incident radiation flux (G), and can be written for a particle laden domain as:
\begin{equation}
\begin{split}
&\frac{\partial}{\partial x_{i}}\left(\Gamma\frac{\partial G}{\partial x_{i}}\right)=\left(\alpha_g+\alpha_p\right)G-4\left(\alpha_g \sigma_{SB} T_{g}^4-\pi E_p \right)\\
&\Gamma = \frac{1}{\alpha_g+\alpha_p+\sigma_p}
\end{split}
\end{equation}

@@

\subsection{Process simulation model}
A 1D discretized model of the furnace evaporator, platen SH, final SH, and subsequent down stream heat exchangers was developed using Flownex SE\textsuperscript{\textregistered} 2021. The model simulates the internal convection heat transfer inside the tubes and the conduction through the tube walls. The model is able to simulate the attemperation flows and momentum transport through the steam/water circuit. The heat exchangers were modelled using a two-phase mixture approach, this assumes that the fluid properties, phase velocities and temperatures are uniform per cross-sectional area. The homogeneous mixture fraction and mixture density are defined in equations (\ref{eqn_vol_frac}) and (\ref{eqn_mix_rho}) respectively.
\begin{gather}
\alpha_H = \frac{\rho_l x}{\rho_lx + \rho_g(1-x)} \label{eqn_vol_frac}\\  
\rho_M = (1-\alpha_H)\rho_l + \alpha_H\rho_g \label{eqn_mix_rho}
\end{gather}
Applying the mixture density the following transport equations are solved per process model component;

@@

The process model is used to determine the required attemperation flow rates in order to achieve the exit steam conditions, the boiler efficiency, and the steam generated for each case. The results of this model aid in determining the best firing combination of burner rows for continuous low-load operation, and the effects the various Cases have on the water-side of the boiler system.

@@

\subsection{Geometry \& process model set-up}
The modelled  boiler is a two-pass sub-critical power boiler with a furnace depth of 13.77 [$m$], a width of 14.01 [$m$] and a height of 64 [$m$]. The CFD geometric model (of Figure \ref{fig_geometry}) makes use of a symmetry plane at half the width of the furnace. This was done to reduce the cell count of the numerical mesh. Both the platen and final SH are modelled as walls, with transverse pitches of 1.143 [$m$] and 0.8 [$m$] respectively. There are three levels of burners located on both the front and rear walls at heights of 11.9 [$m$], 19.3 [$m$] and 26 [$m$]. Figure \ref{fig_geometry} shows the modelled half of the furnace along with the locations of the platen SH, final SH, boundary walls (front, rear and side) and the domains outlet and inlets.\\
\begin{figure} [h!]
\centerline{\includegraphics[scale=0.45]{GEOMETRY}}
\caption{Boiler geometry and layout}
\label{fig_geometry}
\end{figure}

The boiler furnace is fed by 6 mills, each supplying pulverised fuel and primary air (PA) mixture to a burner row consisting of 6 burners. This mixture is injected through the inner burner annulus while the secondary air (SA) is fed through the outer annulus as seen Figure \ref{fig_geometry}.

>>>>

%% Group authors per affiliation:
\author{B.T. Rawlins}
\author{R. Laubscher\corref{mycorrespondingauthor}}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{rlaubscher@sun.ac.za}
\author{P. Rousseau}
\address{Department of Mechanical Engineering, Applied Thermal-Fluid Process Modelling Research Unit, University of Cape Town, Library Rd, Rondebosch, Cape Town, 7701, South Africa}
\address{$^*$ Department of Mechanical Engineering, Stellenbosch University, Stellenbosch Central, Stellenbosch, 7599, South-Africa}

\begin{abstract}
Low-load operation of a 620 $MWe$ sub-critical boiler is analysed with the aid of a co-simulation methodology that incorporates a detail three dimensional computational fluid dynamics (CFD) model together with a one dimensional process model. A discretized one dimensional model of the water/steam circuit was developed for the furnace, the radiant superheaters and the convective/back pass heat exchangers. This is coupled with a detailed CFD model incorporating the furnace and radiant superheaters using a Eulerian-Eulerian reference frame. The coupled model is used to investigate the combustion stability, water/steam side effects, and the radiant heat exchanger operational limits for six different burner firing arrangements at a low boiler load of 32\% of Maximum Continuous Rating. The results show that certain firing arrangements can lead to a high risk of fire-side corrosion and overheating of heat exchanger components. Based on analyses of combustion stability, boiler efficiency and the safe operation of heat exchanger components, a mixed firing arrangement with a higher secondary air mass flowrate for non-firing burners was selected as the best operational strategy at this low load for the boiler under investigation.
\end{abstract}

@@

%\linenumbers

@@

The use of coal-fired power plants (CFPP) for electricity generation is intended to be phased out to reduce the rate of climate change. However, the move to sustainable generation sources poses great challenges for developing countries due to the long transition times and costs involved \cite{ugum2019}. Due to the abundance of coal resources present in Southern Africa, CFPPs are still the dominant power generation source, with approximately 80\% of the energy needs being met using CFPPs \cite{eskom}.\\

The integration of renewable energy sources will push CFPPs from primarily base load operation to a mid-merit/flexible operating protocol, which includes prolonged operation at low-loads. Long term deviation from design conditions can lead to operational inefficiencies affecting combustion stability \cite{Hernik2020}, an increase in harmful emissions \cite{Chang2021}, and the localised overheating of heat exchangers due to insufficient cooling being provided by the internal working fluid \cite{Modlinski2019}.\\

While full scale testing or experimentation on CFPPs is deemed too expensive to pursue, mathematical models that can accurately capture the thermal response of boilers at varying loads can be used to determine the safe and efficient operating limits \cite{Laubscher2019b}. Computational fluid dynamics (CFD) allows for the modelling of full-scale CFPP boilers, at steady-state operating conditions. CFD simulations have been successfully used to model a variety of CFPP boiler types (\cite{Laubscher2019a}, \cite{Gu2020}) and cover various aspects such as pollution control (\cite{Du2017},\cite{Fan2001}), gas-solid flow effects (\cite{Chen2017}) and boiler retrofitting (\citep{Gu2020}, \cite{He2007}).\\

Recent CFD studies investigating low-load operation of CFPP boilers have focused on the combustion stability, harmful emissions and the gas flow-solid flow interactions \cite{Jiang2021}. The works of Belosevic et al \citep{Belosevic2019a} found that the low-load operation of boilers considerably affects the flow and temperature fields, the flame geometry, chemical reactions and concentrations of combustion products.\\

Hernik et al \cite{Hernik2020} investigated the effects of using different mill system configurations at a minimum boiler load of 40\%. The most favourable mill system configuration was selected based on the case that exhibited suitable combustion stability and emission of harmful substances. Similarly, Chang et al \citep{Chang2021} investigated the various firing arrangements of a 630 $MWe$ tangentially fired boiler. A burner angle of -15 $^\circ$ was found to be the optimal arrangement resulting in the best compromise between combustion stability and lower emissions. The aforementioned research specifically investigated combustion and gas-side effects.\\

Various one-dimensional (1-D) process modelling approaches have also been used by researchers to investigate the water and gas side heat transfer interactions. These studies are usually aimed at investigating a transient event, such as a sudden disturbance, start-up, or boiler load ramping \cite{Alobaid2017}. Due to the non-uniformities found in CFPP furnaces which are composed of complex combustion dynamics, gas-solid interactions and  radiation heat transfer phenomena, 1-D process models can not resolve the fireside with sufficient accuracy. However it can adequately resolve the waterside energy and momentum transport in a computationally inexpensive manner.\\

The use of coupled simulations has proven to solve the deficiencies of a full 1-D process model by coupling the fireside CFD results to a 1-D water side model. Laubscher and Rousseau \cite{Laubscher2020} conducted a comprehensive numerical study on the impact of particle radiation properties for high ash coals using ANSYS Fluent v19.2\textsuperscript{\textregistered} and Flownex SE\textsuperscript{\textregistered}, while Yu et al \cite{Yu2019} used a coupled simulation methodology to estimate the superheater (SH) metal temperatures of a 660 $MWe$ tangentially-fired coal boiler.\\

However, to the authors’ knowledge, the integration of a 1-D process model with a detail CFD model has not been used to investigate the steam side operational performance of a CFPP boiler specifically at low-load. The goal of the current work is therefore to investigate the effect of burner firing configuration on various process parameters such as steam temperatures, spray water flowrates and metal temperatures at low-load, using a detailed CFD model on the gas side coupled to a comprehensive process model on the water/steam side.\\

To establish the accuracy of the CFD modelling approach a validation study was first conducted at loads of 100\%, 80\% and 60\% Maximum Continuous Rating (MCR) and compared to actual plant measurements. Thereafter the model was applied to simulate the boiler operation at 32\% of MCR with six different firing configurations.

\section{Mathematical model}
\subsection{Computational fluid dynamics modelling}
\subsubsection{Fluid flow, turbulence and combustion modelling}
The flue gas-side was modelled using a Eulerian framework. The species transport modelling approach was used to approximate the mixture of chemical species in the gas phase. This approach solves a species continuity equation for each constituent present in the mixture. To reduce the computational burden, it was assumed that the various processes were in steady-state. The governing equations for the gas phase are written below in their respective Reynolds.\\
Mass conservation:
\begin{equation}\label{eqn_RANS_mass}
\frac{\partial}{\partial x_{i}}(\rho \bar{u}_{i})=S_{m}.
\end{equation}
Momentum conservation:
\begin{equation}\label{eqn_momentum}
\frac{\partial}{\partial x_{i}}(\rho_{eff} u_{i}u_{j})+\frac{\partial \overline{p}}{\partial x_{j}}=\frac{\partial}{\partial x_{i}}\left[\mu\left\{\frac{\partial u_{j}}{\partial x_{i}}+\frac{\partial u_{i}}{\partial x_{j}}-\frac{2}{3}\delta_{ij}\frac{\partial u_{i}}{\partial x_{i}}\right\}\right]+\frac{\partial}{\partial x_{i}}(-\rho\overline{u_{i}^{'}u_{j}^{'}})+S_m
\end{equation}
Energy conservation:
\begin{equation}\label{eqn_energy}
\frac{\partial }{\partial x_{i}} (u_{i}[\rho E+p])=\frac{\partial }{\partial x_{j}}\left[\lambda\frac{\partial T_{g}}{\partial x_{j}}\right] +S_{h}
\end{equation}
Species transport:
\begin{equation}\label{eqn_species}
\begin{split}
&\frac{\partial}{\partial x_{i}}(\rho u_{j}Y_{k})=-\frac{\partial}{\partial x_{j}}(\vec{J_{k}})+ \sum_r R_{j,r} + S_{k}\\
&k = 1,2,3...N
\end{split}
\end{equation}
To correctly account for the particle inertial effects on the gas phase convection, the model makes use of an effective density which is defined as follows:
\begin{equation} \label{eqn_eff_rho}
	\rho_{eff} = \frac{\rho \rho_p \left( \phi_{mp} + 1 \right)}{\rho \phi_{mp} + \rho_p}
\end{equation}

In the present study the realizable k-$\varepsilon$ turbulence model was utilized to address the turbulence closure problem. This model has been successfully used by researchers (\cite{Belosevic2019a},\cite{Laubscher2019a} and \cite{Modlinski2019}), in modelling the effects of coal-fired swirl burners. The model generally produces higher accuracy results, when compared to the standard k-$\varepsilon$ model, for problems incorporating swirling and separating flows.\\

The process of coal combustion comprises of four sequential steps namely, inert heating and evaporation of moisture, devolatilization, char oxidation and gas phase reactions. Equations (\ref{eqn_vol_rate}) and (\ref{eqn_vol_arrhenuis}) show the single rate kinetic model utilized in this study, to model the devolatilization process.
\begin{gather}
\frac{dm_{vol}}{dt} = R_{vol}(m_{0,vol}-m_{vol}) \label{eqn_vol_rate} \\
\begin{split}
&R_{vol} = A_{vol}exp\left(\frac{E_{a,vol}}{RT_p}\right)\\
&A_{vol} = 2\times10^5 [s^{-1}]\,\,\,\,\,\,\,\,\,\,E_{a,vol} = 6.7\times10^7 [J/kmol] \label{eqn_vol_arrhenuis}
\end{split}
\end{gather}

A devolatilization temperature of 553 [$K$] \citep{Ranade2015} along with the kinetic parameters (equation \ref{eqn_vol_arrhenuis}) of Sheng et al \cite{Sheng2004} were utilized in the present study.\\

The char oxidation process is modelled using the diffusion-kinetics limited model developed by Baum and Street \cite{Baum1971}, which is given in equation (\ref{eqn_char_rate}). The product species of the char oxidation reaction was set to $CO$ as shown in equation (\ref{eqn_CO_reaction}). 
\begin{gather}
\frac{dm_{char}}{dt} = -A_p p_{O_{2}} \frac{R_{diff}R_c}{R_{diff} + R_c}  \label{eqn_char_rate}\\
C_{(s)}+0.5O_{2(g)}\to CO_{(g)} \label{eqn_CO_reaction}
\end{gather}
The diffusion and kinetic rates of equation (\ref{eqn_char_rate}) are defined in equations (\ref{eqn_char_diff_rate})  and (\ref{eqn_char_kin_rate}) with the kinetic parameters again taken from the works of Sheng et al \citep{Sheng2004}.
\begin{gather}
R_{diff} = \frac{5\times10^{-12}}{d_p} \left(\frac{T_g+T_p}{2}\right)^{0.75} \label{eqn_char_diff_rate}\\
\begin{split}
&R_{c} = A_{c}exp\left(\frac{E_{a,c}}{RT_p}\right)\\
&A_{c} = 0.0053 [kg/m^2sPa]\,\,\,\,\,\,\,\,\,\,E_{a,c} = 8.37\times10^7 [J/kmol]
\end{split}
 \label{eqn_char_kin_rate}
\end{gather}

The turbulence-chemistry interactions of the gas phase reactions were approximated using the eddy-dissipation-finite rate model used in ANSYS Fluent v19.5\textsuperscript{\textregistered} which calculates three rates, namely chemical reaction rate, turbulent production eddies dissipation rate and reaction eddies dissipation rate. It then applies the minimum of the three for the source terms calculations. A description of the CFD gas phase reactions of the boiler under consideration, using the same coal, was previously published in the works of Laubscher and Rousseau \cite{Laubscher2019b}.

\subsubsection{Particle modelling}
The particles are modelled using a Eulerian reference frame, similar to the studies of Knaus et al \cite{Knaus2001a} and Benim et al \cite{Benim2005}. Both successfully used a Eulerian-Eulerain (EE) model to capture the characteristics of coal combustion and furnace heat transfer with adequate accuracy. The pseudo particle mass concentrations transported into the domain are modelled using the general scalar field transport equation with the necessary modifications to account for heat and mass transport \cite{Versteeg2007}. The pseudo-particles scalar fields are used to define the fuel characteristics based on the proximate analysis composition, namely consisting of moisture, volatile matter, fixed carbon and ash. The scalar field equations are provided in Table \ref{tab_scalars}.\\

@@

The energy transport of the pseudo particle phase, is captured by defining a particle phase energy balance equation, which in turn uses the particle enthalpy.
\begin{equation}\label{eqn_phi_hp}
\frac{\partial}{\partial x_{i}}(\rho u_{i} \phi_{hp})=\left(f_{heat}\frac{dm_{c}}{dt}h_{rxn} + \dot{Q}_{rad} + \dot{Q}_{conv} - \frac{dm_{evap}}{dt}h_{fg}\right)\frac{1}{V}
\end{equation}

The equation accounts for all the processes associated with energy transport to the particle, namely convection $\left(\dot{Q}_{conv}\right)$, radiation $\left(\dot{Q}_{rad}\right)$, latent heat transport $\left(\frac{dm_{evap}}{dt}h_{fg}\right)$ and near surface char oxidation $\left(f_{heat}\frac{dm_{c}}{dt}h_{rxn}\right)$. This gives the model the ability to track the particle temperature in the domain, which distinguishes it from the thermal equilibrium approach incorporated by previous studies using an EE approach (\cite{Benim2005}, \cite{Vicente2003} and \cite{Cai2015}). The particle temperature is important in describing the sequential steps found in modelling combustion processes, especially at low boiler loads where mixing and ignition become problematic. To solve the additional transport equations and their source terms, C programs were developed.

\subsection{Heat transfer modelling}
Radiation heat transfer is the dominant form of heat transfer found in industrial furnaces \citep{Basu2000} and is solved by applying the gray-participating-gas and particle medium configuration of the radiation transport equation (RTE) \cite{Modest2013} shown in equation (\ref{eqn_RTE}).
\begin{equation}\label{eqn_RTE}
\frac{d I(\vec{r},\hat{s})}{ds} = \alpha_g \frac{\sigma_{SB} T_{g}^4}{\pi}-(\alpha_g+\alpha_p+\sigma_p)I(\vec{r},\hat{s}) + \frac{\sigma_p}{4\pi}\int_{4\pi}I(\vec{r},\hat{s})\Phi d \Omega
\end{equation}
In the present work the RTE is solved using the P1 model. Ranade and Gupta \cite{Ranade2015} illustrated minimal differences between the two common radiation models (namely the P1 and discrete ordinates (DO)) for the resultant wall heat transfer rate values when modelling a 210 $MWe$ CFPP boiler. The P1 radiation model can include the effects of particle absorption ($\alpha_p$) and scattering ($\sigma_p$) as well as gas mixture absorption ($\alpha_g$). The P1 model transport variable is the incident radiation flux (G), and can be written for a particle laden domain as:
\begin{equation}
\begin{split}
&\frac{\partial}{\partial x_{i}}\left(\Gamma\frac{\partial G}{\partial x_{i}}\right)=\left(\alpha_g+\alpha_p\right)G-4\left(\alpha_g \sigma_{SB} T_{g}^4-\pi E_p \right)\\
&\Gamma = \frac{1}{\alpha_g+\alpha_p+\sigma_p}
\end{split}
\end{equation}

@@

\subsection{Process simulation model}
A 1D discretized model of the furnace evaporator, platen SH, final SH, and subsequent downstream heat exchangers was developed using Flownex SE\textsuperscript{\textregistered} 2021. The model simulates the internal convection heat transfer inside the tubes and the conduction through the tube walls. The model is able to simulate the attemperation flows and momentum transport through the steam/water circuit. The heat exchangers were modelled using a homogeneous two-phase mixture approach, which assumes that the fluid properties, phase velocities and temperatures are uniform per cross-sectional area. The homogeneous mixture fraction and mixture density are defined in equations (\ref{eqn_vol_frac}) and (\ref{eqn_mix_rho}) respectively.
\begin{gather}
\alpha_H = \frac{\rho_l x}{\rho_lx + \rho_g(1-x)} \label{eqn_vol_frac}\\  
\rho_M = (1-\alpha_H)\rho_l + \alpha_H\rho_g \label{eqn_mix_rho}
\end{gather}
Applying the mixture density the following transport equations are solved per process model component;

@@

The process model is used to determine the required attemperation flow rates to achieve the exit steam conditions, boiler efficiency, and steam generation for each case. The results of this model aid in determining the best firing combination of burner rows for continuous low-load operation, and the effects on the water-side of the boiler system.

@@

\subsection{Geometry \& process model set-up}
The modelled  boiler is a two-pass sub-critical power boiler with a furnace depth of 13.77 [$m$], width of 14.01 [$m$] and height of 64 [$m$]. The CFD geometric model (of Figure \ref{fig_geometry}) makes use of a symmetry plane at half the width of the furnace. This was done to reduce the cell count of the numerical mesh. Both the platen and final SH are modelled as solid wall panels, with transverse pitches of 1.143 [$m$] and 0.8 [$m$] respectively. There are three levels of burners located on both the front and rear walls at heights of 11.9 [$m$], 19.3 [$m$] and 26 [$m$]. Figure \ref{fig_geometry} shows the modelled half of the furnace along with the locations of the platen SH, final SH, boundary walls (front, rear and side) and the domain outlet and inlets.\\
\begin{figure} [h!]
\centerline{\includegraphics[scale=0.45]{GEOMETRY}}
\caption{Boiler geometry and layout}
\label{fig_geometry}
\end{figure}

The boiler furnace is fed by six mills, each supplying pulverised fuel and primary air (PA) mixture to a burner row consisting of six burners. This mixture is injected through the inner burner annulus while the secondary air (SA) is fed through the outer annulus as seen Figure \ref{fig_geometry}.\\

The process model of the boiler configuration is shown in Figure \ref{fig_flownex}. The process model includes all the heat exchangers up to and downstream of the final SH, which include the secondary reheater (RH2), primary SH (SH1), primary reheater (RH1), economiser (EC) and the SA air heaters (SA-AH). The model includes all the relevant attemperators (ATT1, ATT2 and ATT-RH), inlets and outlets. The process model is used to determine the required attemperation flowrates and water/steam side thermal response. The furnace water-walls are represented by a single lumped pipe flow component and forms part of the natural circulation system that includes the downcomers and steam drum. As with the furnace walls, the platen and final SHs are similarly represented by a single lumped parameter pipe flow component, interconnected with nodes that introduce the attemperation flows to the water/steam side.\\
